---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# tfds

<!-- badges: start -->
<!-- badges: end -->

tfds is an R interface to TensorFlow Datasets and provides a collection of 
datasets ready to use with TensorFlow and Keras. It handles downloading and
preparing the data and constructing a TensorFlow Dataset.

## Installation

tfds is not currently on CRAN. The development version can be installed from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("rstudio/tfds")
```

After installing the R package, you need to install the `tensorflow_datasets`
python module with:

```{r}
tfds::install_tfds()
```


## Example

`tfds_load` is a convenience method that's the simplest way to build and load a 
`tf_dataset`. 

Below, we load the MNIST training data. It downloads and prepares the data, unless
you specify `download=FALSE`. Note that once data has been prepared, subsequent 
calls of load will reuse the prepared data. You can customize where the data is 
saved/loaded by specifying `data_dir=` (defaults to `~/tensorflow_datasets/`).

```{r example}
library(tfds)
mnist <- tfds_load("mnist")
mnist
```

This will use the default version of the dataset. It's however recommended to specify the dataset version when loading:

```{r}
minst <- tfds_load("mnist:1.*.*")
```

We can build a simple model using `mnist` and Keras with:

```{r}
library(keras)
library(tfdatasets)

model <- keras_model_sequential() %>% 
layer_flatten(input_shape = c(28,28,1)) %>% 
  layer_dense(512, activation = "relu") %>% 
  layer_dense(10, activation = "softmax")

model %>% 
  compile(
    loss = "sparse_categorical_crossentropy", 
    optimizer = "adam", 
    metric = "accuracy"
  )

train_dataset <- mnist$train %>% 
  dataset_shuffle(1024) %>% 
  dataset_batch(32) %>% 
  dataset_map(unname)

test_dataset <- mnist$test %>% 
  dataset_batch(32) %>% 
  dataset_map(unname)

model %>% 
  fit(train_dataset, validation_data = test_dataset, epochs = 5)
```

